### 2020-08-17 7_conclusion.tex
Update acknowledgements to include all developers.

This material is based upon work supported by the U.S. Department of
Energy, Office of Science, Office of ASCR, under the contract number
DE-AC02-76SF00515, by National Science Foundation under Grant
No. ACI-1450300, and the Exascale Computing Project (17-SC-20-SC), a
collaborative effort of the U.S. Department of Energy Office of
Science and the National Nuclear Security Administration, under prime
contract DE-AC05-00OR22725, and UT Battelle subawards 4000151974 and
89233218CNA000001. Experiments on the Cori supercomputer were
supported by the National Energy Research Scientific Computing Center,
a DOE Office of Science User Facility supported by the Office of
Science of the U.S. Department of Energy under Contract
No. DE-AC02-05CH11231, and experiments on Piz Daint were supported by
the Swiss National Supercomputing Centre (CSCS) under project ID d80.

>>>>

This material is based upon work supported by the U.S. Department of
Energy, Office of Science, Office of ASCR, under the contract number
DE-AC02-76SF00515, by National Science Foundation under Grant
No. ACI-1450300, and the Exascale Computing Project (17-SC-20-SC), a
collaborative effort of the U.S. Department of Energy Office of
Science and the National Nuclear Security Administration, under prime
contract DE-AC05-00OR22725, and UT Battelle subawards 4000151974 and
89233218CNA000001. Experiments on the Cori supercomputer were
supported by the National Energy Research Scientific Computing Center,
a DOE Office of Science User Facility supported by the Office of
Science of the U.S. Department of Energy under Contract
No. DE-AC02-05CH11231, and experiments on Piz Daint were supported by
the Swiss National Supercomputing Centre (CSCS) under project ID
d80. A special thanks to thank Katie Antypas for her support.

The authors would like to thank the developers of the programming
systems tested in this paper. Their support enabled us to produce
high-quality implementations of the systems under study. The
developers consulted include (alphabetically by system): Chapel:
Bradford L.~Chamberlain and Elliot Ronaghan; Charm++: Laxmikant Kalé
and Sam White; Dask: Matthew Rocklin; MPI: Samuel K.~Gutiérrez and Wei
Wu; OmpSs: Víctor López and Vicenç Beltran Querol; OpenMP: Alejandro
Duran and Jeff R.~Hammond; PaRSEC: George Bosilca and Qinglei Cao;
Realm: Seema Mirchandaney and Sean Treichler; Regent: Michael Bauer,
Wonchan Lee, Seema Mirchandaney and Elliott Slaughter; Spark: Matei
Zaharia; StarPU: Samuel Thibault; Swift/T: Justin M.~Wozniak;
TensorFlow: Jing Dong, Peter Hawkins and Mingsheng Hong; X10: David
Grove, Sara S.~Hamouda and Josh Milthorpe.
